---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dhis2r

<!-- badges: start -->
<!-- badges: end -->

The goal of dhis2r is to provide a wrapper for the Dhis2 web api

## Installation

You can install the development version of dhis2r from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pearldatafirm/dhis2r")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(dhis2r)
## basic example code
```

You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
